\vspace{-1.5em} \bf Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-06-05 paper.tex
Start on details for false positives table

>>>>

\subsection{False positive recombinants}
The Long and Wide ARGs both contain several recombination nodes that are
ancestral to large numbers of samples, and are almost certainly
artefactual. The

\begin{table} \centering
\begin{tabular}{lllll}
Strain & Lineage & Descendants & HMM Cost & Lineage rank\\
Germany/HH-RKI-I-061284/2021 & B.1.617.2 & 178405 & 17 & 2 \\
India/ILSGS00961/2021   & B.1.617.2 & 177649 & 25  & 7  \\
Denmark/DCGC-281594/2021 & BA.2.9 & 127227 & 32  & 1\\
USA/NJ-GBW-EWR000001/2021 & BA.3 & 127230 & 25 & 1\\
\end{tabular}
\caption{\label{tab:false_positive}
False positive recombination events.}
\end{table}

Further study is required to systematically identify likely false
positive
